Storing messages with multipartite neural cliques

### 2014-07-18 Articles/article.tex
...

		We can for example fix a maximum number of steps to the algorithm or even stop at one point if $\tilde{x}_{t+1} = \tilde{x}_t$. The number of iterations can of course improve the retrieval rate.

@@

	We first compute the theoretical density of the network, that is to mean the probability for a random edge $(l, l')$ to be present in the network (i.e. $W_{ll'} = 1$). We then express the theoretical error rate after one iteration of the retrieving rule in function of the density. All this computations (on error rates) are done assuming connections between units are independent, which is false but is a convenient approximation that gives results matching very closely results from simulations.

@@

	Suppose we are trying to retrieve a message where $c_e$ clusters have been erased. %(i.e. all units in those clusters are set to $0$).
	Thanks to the memory effect $\gamma$, activated units in a non-erased cluster stay activated and are the only ones doing so in their cluster (as the others can't achieve a higher score thanks to not being already activated). For units in erased clusters, the maximum attainable score is $a(c - c_e)$. Units corresponding to the original message achieve this score. Since scores follow a binomial law, the probability for a unit $v$ to achieve the maximum score in such a cluster, that is to mean $a(c-c_e)$ is $d^{a(c-c_e)}$.

@@

	As information on a message is shared across connections with multiple activated units per cluster, such networks are more resilient to damages (for one message information is carried by $a^2 {c \choose 2}$ edges. $v_c$ will indicate a correct unit that should be activated, $v$ the other type of units.

>>>>

		We can for example fix a maximum number of steps to the algorithm or stop at one point if $\tilde{x}_{t+1} = \tilde{x}_t$. Increasing the number of iterations can of course improve the retrieval rate.

@@

	We first compute the theoretical density of the network, that is to mean the probability for a random edge $(l, l')$ to be present in the network (i.e. $W_{ll'} = 1$). We then express the theoretical error rate after one iteration of the retrieving rule in function of the density. All this computations (on error rates) are done assuming existences of edges between random units are independent, which is false but is a convenient approximation that gives results matching very closely results from simulations.

@@

	Suppose we are trying to retrieve a message where $c_e$ clusters have been erased. %(i.e. all units in those clusters are set to $0$).
	Thanks to the memory effect $\gamma$, activated units in a non-erased cluster stay activated and are the only ones being so in their cluster (as the others can't achieve a higher score thanks to not being already activated). For units in erased clusters, the maximum attainable score is $a(c - c_e)$. Units in erased clusters corresponding to the original message achieve this score. Since scores follow a binomial law, the probability for a random unit to achieve the maximum score in such a cluster, that is to mean $a(c-c_e)$ is $d^{a(c-c_e)}$.

@@

	As information on a message is shared across edges with multiple activated units per cluster, such networks are more resilient to damages (for one message information is carried by $a^2 {c \choose 2}$ edges. $v_c$ will indicate a correct unit that should be activated, $v$ the other type of units.
